Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-01 PaperVictor.tex
Revise up to the first experimental results

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the reflectance ($\braket{R_{\text{ave}}}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano}   of PS-based
mirrors  averaged over a wide wavelength
and angular range, for different
porosity contrasts, and we minimize their thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
structures and by \textit{stacking} sub-mirrors. We found \notaL{No
  estoy seguro del tiempo} that
chirped structures were better suited for the Vis stacked
sub-mirrors for the NIR region. We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

In this section we present compare the calculated and measured reflectance
spectra at different incidence angles in the regions of interest. In the first
subsection, the design and optimization of R$_{\text{ave}}$ of \textit{chirped}
photonic structures is presented, and next subsection the design of the structure is
analyzed through sub-mirrors stacks.

\notaL{Quizás esto se pueda incluir por aquí.:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
}
\subsection{Chirped-type Bragg mirrors}

The generic form of the expression that modulates the design of photonic
structure is:
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left( x_{j}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$, $\lambda_{\max }$ and $\lambda_{j}$ correspond
to the minimum, maximum, and design wavelengths to which the $j$-th period
is tuned, respectively, and $f\left( x_{j}\right) $ represents any
normalized function that modulates the thickness. Here $x_{j}=\frac{j}{N_{p}}$ being
$j$ the $j$-th period and $N_{p}$ the total number of periods that the structure
will contain. Only restriction for $f\left( x_{j}\right) $ is that it has to be an
increasing function, due to the high absorption of PS in the ultraviolet region
which decreases in the visible and becomes negligible in the near infrared. So, the
first periods are syntonized in the UV-Vis regions. This work shows the analysis
of following functions:
\begin{equation}
f_{1}\left( x\right) =x^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left( x\right) =A\left( x^{\alpha }+x^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left( x\right) =Ax^{\alpha }\left( 1-x\right) +x^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize. The function
$f_{1}$ (Eq. (\ref {F1})) represents the simplest profiles. The restrictions
for the values $\alpha$ are that they must be positive and they must not be
extremely large or small. In these cases, mirrors that reflect in
$\lambda_{\text{min}}$ or $\lambda _{\text{max}}$, respectively, will be obtained. Eq.
(\ref{F2}) is formed by the average of two functions of type $f_{1}$ with different
powers. The function $f_{3}$ (Eq. (\ref{F3})) was designed so that the first and second
additions predominate the short and long wavelengths, respectively. The
R$_{\text{ave}}$ of the structures is calculated in
the wavelength range from 350 to 1400 nm and from 0 to 90${{}^\circ}$ angle of
incidence. The optimized parameters using a porosity contrast of $51/76\%$ are shown
in Table 1 and in the supplementary information they appear for the porosity
contrasts of $30/76\%$ and $42/76\%$.
\begin{table}
\caption{ Design parameters obtained after the optimization of functions (Eqs.
(\ref{F1}) - (\ref{F3})) for maximum average reflectance and minimum thickness }%
\includegraphics[width=\textwidth]
{F2TableOptimized.pdf}
\end{table}

According to the values shown in table I, the structure (named as ST-A) that has the
maximum average reflectance with the minimum thickness is the one designed
with the function $f_{3}$ (Eq. (\ref{F3})). Thus, the first and last periods
are tuned to 320 and 1400 nm, respectively. The complete distribution of the
periods is presented in Fig. \ref{Fig2}(a).
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]
{F3OptimizedVis.pdf}
\end{center}
\caption{(a) Distribution of $\protect\lambda_{j}$ in the $j$-th period for
the design of the 63-period multilayer structure. (b) Mapping of the average
reflectance of the structures designed with different values{}of $%
\protect\alpha $ and $N_{p}$ parameters. It is verified that the parameters
obtained during the optimization are adequate ($\protect\alpha =1.23$ and $%
N_{p}=63$). (c) Mapping the calculated reflectance for non polarized light of the
designed structure with the optimized values. (d) Comparison of reflectance spectra
calculated and measured at different angles of incidence. The gray band indicates the
region in which the reflectance is greater than 95\%. Inset shows the
top view photograph of the synthesized structure.}
\label{Fig2}
\end{figure}
To verify that the values obtained are optimal, in Fig. \ref{Fig2}(b), the average
reflectances of the photonic structures designed with different parameters are mapped
and, indeed, the values are in the area where R$_{\text{ave}}$ is maximum. Here, the
parameters $\lambda_{\text{min}}$, $\lambda_{\text{max}}$, $\beta$ and $A$ were
adjusted, while $N_{p}$ and $\alpha$ varied from 30 to 200 periods and from 0.4 to 1.3,
respectively. The calculated reflectance, R$\left( \lambda ,\theta \right) $, of the
photonic structure is shown in Fig \ref{Fig2}(c). Here, the wavelength and incidence
angle cover the ranges from 350 to 1400 nm, and from 0${{}^\circ}$ to 90${{}^\circ}$,
respectively. Calculations indicate that the structure has a localized omnidirectional
band gap from 1000 to 1200 nm, taken with a reflectance greater than 95$\%$. Due to
experimental limitations, reflectance spectra for non polarized light are shown in all results. In Fig. \ref{Fig2}(d), the calculated and measured reflectance is compared
at 10${{}^\circ}$, 20${{}^\circ}$, 30${{}^\circ}$, 40${{}^\circ}$, 50${{}^\circ}$
and 60${{}^\circ}$ of incidence. In this angular range, the structure has a
quasi-omnidirectional band gap (R$\left(\lambda,\theta\right)>95\%$) located from
980 to 1340 nm. The numerical and experimental spectral line shapes at different
angles are in good agreement. For wavelengths greater than 700 nm and lying between
10${{}^\circ}$ to 40${{}^\circ}$ of incidence angle, the difference in spectra is
less than $5\%$. For angles of incidence greater than 40 degree, although their
characteristics are similar, the measured spectrum demonstrates relatively less
reflectance than calculated reflectance. This difference can be attributed, in part,
to the scattering of light between each of the actual interfaces, which generally
have some roughness \cite{Theiss1994,Chavez2020}.

>>>>

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the reflectance $\braket{R}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano}   of PS-based
mirrors  averaged over a wide wavelength
and angular range, for different
porosity contrasts, and we minimize their thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
structures and by \textit{stacking} sub-mirrors. We found \notaL{No
  estoy seguro del tiempo} that
chirped structures were better suited for the Vis stacked
sub-mirrors for the NIR region. We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

In this section we presents optimized calculations of the reflectance
of different multilayered omnidirectional wide-band mirrors and we
compare the results to spectra taken from
the corresponding samples at several angles of
incidence. Sec. \ref{ss:chirped} is devoted to chirped-type Bragg
mirrors while Sec. \ref{ss:stacked} is devoted to structures made of
stacked sub-mirrors.

\notaL{Quizás esto se pueda incluir por aquí.:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you
like. {\tiny The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}.} The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
}
\subsection{Chirped-type Bragg mirrors}\label{ss:chirped}

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f(j/N_p)),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and {\em
  design} wavelengths respectively, $N_p$ is the index of the deepst
pair of layers and $f(x)$ is some smooth function
that goes from 0 to 1 as its argument goes from surface ($x=0$) to the
substrate ($x=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region
which decreases in the visible and becomes negligible in the near
infrared, so, the
first periods are syntonized in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left( x\right) =x^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left( x\right) =A\left( x^{\alpha }+x^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left( x\right) =Ax^{\alpha }\left( 1-x\right) +x^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize. The function
$f_{1}$ (Eq. (\ref {F1})) represents simple increasing profiles,
restricting  $\alpha>0$. The functions $f_2$ are arithmetic averages
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $beta$ \notaL{A ¿no debe ser 1/2 a fuerza, para
  que $f_2(1)=1$?}. The functions $f_{3}$ (Eq. (\ref{F3})) are
designed so that the power $\alpha$ dominates close to the surface and
the power $\beta$ close to the substrate, to allow different behaviors
at the UV and at the IR end of the spectrum. The reflectance
$R(\lambda,\theta)$ of the resulting structures was calculated in
the wavelength range from 350 to 1400 nm and for angles of incidence
from normal ($0^\circ$)  to grazing ($90^\circ$) incidence and
averaged to yield $\braket{R}$. The parameters $\alpha$, $\beta$
and $\gamma$ were then optimized to maximize the average
reflectance. The calculations were done using the Perl Data Language
(PDL) and its interface to the MINUIT minimization
package\cite{minuit}.The optimized parameters corresponding to a
porosity contrast of
51/76\% are shown
in Table 1.  In the supplementary information we include the
parameters for porosity contrasts of $30/76\%$ and $42/76\%$.
\begin{table}
\includegraphics[width=\textwidth]{F2TableOptimized.pdf}
\caption{Optimized parameters yielding the highest average reflectance
  $\braket{R}$  for the profile classes $f_1$, $f_2$ and $f_3$ (Eqs.
  (\ref{F1}) - (\ref{F3}))}
\end{table}
\notaL{Sugiero poner aquí una tabla de latex, editable, en lugar de
  una figura}
\notaL{No es claro en el texto cómo se obtiene $N_p$. Se mencionaba
  una minimización del ancho, pero no recuerdo cómo se minimizó a la
  vez que se maximizaba la reflectancia. ¿Fue minuit? ¿Fue a ojo?}

According to table I, the structure (named as ST-A)\notaL{Este nombre
  no está en la tabla. ¿Qué significa el acrónimo?} that has the
maximum average reflectance with the minimum thickness is the one designed
with the function $f_{3}$ (Eq. (\ref{F3})) with parameters
$\alpha=1.23$, $\beta=0.54$ and $A=0.18$, which is shown in
Fig. \ref{Fig2}(a). \notaL{Si queremos que $x_j$ vaya de 0 a 1 habría
  que numerar $j$ de 0 a $N_p-1$, y dividir entre $N_p-1$ en lugar de 1 a $N_p$ y
  dividir entre $Np$. Parece que no lo hiciste así, entonces habría que
  revisar un poco la discusión arriba}.
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{F3OptimizedVis.pdf}
\end{center}
\caption{(a)Design wavelength $\lambda_{j}$ vs. period number $j$-th
  for the optimized structure ST-A with 63-periods.\notaL{Parece un
    poster miniatura. ¿La ilustración a la derecha está a escala o
    es esquemática? ¿La necesitamos? Está tan chica que es ilegible}
  (b) Average reflectance of the structures designed with different
  values of $\alpha$ and $N_{p}$.\notaL{Por qué en la misma figura?
    ¿Cuál es el propósito de incluir esta? Cambia el cbrange para que
    el color diga algo. Se ve todo rojo uniforme.} It is verified that the
  parameters obtained during the optimization are adequate ($\alpha
  =1.23$ and $N_{p}=63$).\notaL{Este comentario va en el texto, no en
    el pie de figura} (c) Reflectance for non polarized light of the
  optimized structure. (d) Comparison of the reflectance spectra
  calculated and measured at different angles of incidence. The gray band indicates the
  region in which the reflectance is greater than 95\%. Inset shows the
  top view photograph of the synthesized structure.\notaL{En mi
    humilde opinión son demasiadas figuras en una sola, no
    claramente relacionadas entre sí.}}
\label{Fig2}
\end{figure}
In Fig. \ref{Fig2}(b)
we show $\braket{R}$ for different values of $N_p$ and
$\alpha$ to illustrate its dependence on the parameters, and
to verify that our optimized values correspond indeed to the maximum. Here, the
parameters $\lambda_{\text{min}}$, $\lambda_{\text{max}}$, $\beta$ and $A$ were
adjusted, while $N_{p}$ and $\alpha$ varied from 30 to 200 periods and from 0.4 to 1.3,
respectively. \notaL{Ya no me quedó claro. Hay que decir arriba cuales
  son los parámetros que se variaron durante la optimización original. ¿Fueron
  $N_p$, $\lambda_{min}$, $\lambda_{\max}$, $A$, $\alpha$ y $beta$,
  todos ellos? Creo que no es claro. Si fue así, hay que distinguir
  las longitudes de onda del ajuste de las del rango en que
  optimizaste la reflectancia}
The calculated reflectance, $R(\lambda ,\theta)$ of the optimized
photonic structure is shown in Fig \ref{Fig2}(c) for wavelengths and incidence
angles covering the ranges from 350 to 1400 nm, and from $0^\circ$ to $90^\circ$,
respectively. Calculations indicate that the structure is an omnidirectional
mirror with a  reflectance $R>0.95$ within a band from 1000 to 1200
nm. \notaL{La zona gris en la figura va más allá de 1200.} We
fabricated a sample corresponding to our
optimized structure and measured its reflectance spectra at several
incidence angles $\theta$. Due to
experimental limitations, we restrict our results to the case of
non-polarized light.
In Fig. \ref{Fig2}(d), the calculated and
measured reflectance are compared
for $\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$, $50^\circ$
and $60^\circ$. In this angular range, the structure has a
quasi-omnidirectional band gap (R$\left(\lambda,\theta\right)>95\%$) located from
980 to 1340 nm. \notaL{Aquí hay un error: el experimento salió ¡mejor
  que la teoría! (ver arriba) Algo hay mal en la descripción, pues la
  figura muestra al experlimento abajo de la teoría.}  The
numerical and experimental spectral line shapes at different
angles are in good agreement. For $\lambda>700$nm and
$10^\circ<\theta<40^\circ$ the spectra differs by
less than $5\%$. For $\theta>40^\circ$ both spectra agree
qualitatively but the measured reflectance is lower that than the
calculated one. This difference can be attributed, in part,
to the scattering of light at the actual interfaces, which generally
have some roughness \cite{Theiss1994,Chavez2020} which we have not
accounted for in our theory.\notaL{Quizás aquí puedas citar el
  artículo de Guillermo Ortiz y mío reciente {\em Rough 1D  Photonic
    Crystals: a transfer matrix approach}, Leandro Missoni, Guillermo
  Ortiz, María Martinez Ricci, Victor Toranzos y W. Luis Mochan,
  Optical Materials {\bf 109}, 110012 (2020)
{\tt https://doi.org/10.1016/j.optmat.2020.110012}}

\notaL{Aquí voy.}
